---
main_topsize: 0.2 #percent coverage of the poster
main_bottomsize: 0.1
#ESSENTIALS
title: '**A Better Reproducible Poster Title**'
author:
  - name: '**W. Brent Thorne**'
    affil: 1
    main: true
    orcid: '0000-0002-1099-3857'
    twitter: brentthorne18 
    email: bthorne2@brocku.ca
  - name: Another G. Contributor
    affil: 2
    main: true
    email: 'ag.con@posterdown.net'
  - name: Person Three
    affil: 3
  - name: Person Four
    affil: 2
  - name: Person Five
    affil: 3
  - name: Person Six
    affil: 3
  - name: A. Seventh Author
    affil: 2
affiliation:
  - num: 1
    address: Department of Earth Science, Brock University
  - num: 2
    address: Department of Graphics and Layouts, University of Posters; Canada
  - num: 3
    address: Another Institute of a place where work gets done, Earth, Milky Way
main_findings:
  - "Make **better posters** with RMarkdown + **posterdown**."
logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
logocenter_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/qr-code-black.png
output: 
  posterdown::posterdown_betterport:
    self_contained: false
    pandoc_args: --mathjax
    number_sections: false
bibliography: packages.bib
link-citations: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html") 
```

# Introduction

This is the `posterdown_betterport` template for the {posterdown} package! I was inspired by the twitter thread of [Mike Morrison](https://mobile.twitter.com/mikemorrison/status/1110191245035479041) and wanted to apply the `#betterposter` concept to the reproducible (yet simple to use) functionality of the {posterdown} package [@R-posterdown]. If you're not an R user don't sweat as you do **NOT** need to use it at all! Feel free to use only the Markdown functionality of this package :)

```{r, include=FALSE}
knitr::write_bib(c('posterdown', 'rmarkdown','pagedown'), 'packages.bib')
```

## Objectives

1. Pick a template layout.
2. Write/ create your poster content distraction free.
3. Let posterdown do its thing!

# Methods

I will show here how to include poster elements that may be useful, such as an equation using mathjax:

$$
E = mc^2
$$

To reference a citation you can add your `.bib` file to the working directory and name it in the YAML metadata or generate an automated one as done here, then you only need to reference the label value in the `.bib` file. For example this package is built on top of the wonderful {pagedown} package and I will cite it at the end of this sentance using this in the rmd `[@R-pagedown]` [@R-pagedown].

To get a better understanding of how to include features like these please refer to the {posterdown} [wiki](https://github.com/posterdown/wiki).

**_Now on to the results!_**

# Results

1. Does average performance vary across format type, ignoring all other aspects of the stimuli?

```{r assignment7-org, message=FALSE}
# Create plot comparing reaction time and accuracy across conditions
suppressWarnings(
  prob_7<-probability_task %>%
    group_by(condition) %>%
    summarise(across(c(rt, correct), mean, na.rm = TRUE)) %>%
    pivot_longer(c(rt, correct))
)
```
```{r assignment7-plot, out.width='60%', out.height = '36%', message=FALSE}
prob_7%>%
    ggplot(aes(y = value, x = condition)) +
    geom_point(color = "red") +
    facet_wrap(~name, scales = "free") +
  # Improve readability of condition labels
    scale_x_discrete(labels = c(
    "blob_shifted" = "Shifted Blob Task",
    "blob_stacked" = "Stacked Blob Task",
    "dots_EqSizeRand" = "Equal Size Random Dot Task",
    "dots_EqSizeSep" = "Equal Size Separated Dot Task"
  )) +
  theme_minimal() +
  labs(title = "Reaction Time and Accuracy by Condition") +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    strip.text = element_text(size = 12),
    axis.text = element_text(size = 10)
  )

```
Average performance seems to vary. It seems that the tasks with the lower reaction times have higher accuracies.

2. How are reaction time and accuracy related?
```{r assignment8-org, out.width='60%', out.height='36%',message=FALSE}
# Calculate average RT and accuracy per subject and condition
prob_task_wrangled <- probability_task %>%
  group_by(SubID, condition) %>%
  summarize(rt = round(mean(rt, na.RM = TRUE)),
            correct = round(mean(correct, na.RM = TRUE),3),
            .groups = "drop")
```
```{r assignment8-plot, out.width='60%', out.height = '36%', message=FALSE}
# Create scatterplot with regression lines
ggplot(prob_task_wrangled, aes(x = rt, y = correct, color = condition)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~condition, labeller = labeller(
    condition = c(
      "blob_shifted" = "Shifted Blob Task",
      "blob_stacked" = "Stacked Blob Task",
      "dots_EqSizeRand" = "Equal Size Random Dot Task",
      "dots_EqSizeSep" = "Equal Size Separated Dot Task."
    )
  )) +
  theme_minimal() +
  labs(
    title = "Reaction Time vs Accuracy by Condition (Facets)", 
    x = "Reaction Time", 
    y = "Proportion Correct"
  )
```


# References
